Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-09 ms.tex
writing in emission prediction and conclusions sections

\section{Low-frequency Emission Predictions}
% compare 100-217 GHz predictions using my model versus Planck Collaboration
% single-MBB model

@@

%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
An important difference between our maps and those of \cite{planckdust} is our 
use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
clearly visible in the \cite{planckdust} maps.

%we actually have 6.1' arcminute resolution
It is true that we have smoothed the input intensity maps for this study 
to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
\cite{planckdust} maps. However, as is apparent from figure 
\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.

%\subsection{Validation with FIRAS}

@@

\section{Conclusions}
\label{sec:conclusion}
% should mention that one definitive improvement of this work relative
% to FDS99 is that there are uncertainty/covariances provided for
% the derived parameters !!!!

>>>>

\section{Low-frequency Emission Predictions}
FDS99 originally performed their two-component versus single-MBB dust SED 
analysis for the sake of accurately forecasting low-frequency CMB foregrounds.
The need for accurate CMB foreground predictions, especially in the 100-150 GHz
frequency range, has been highlighted of late by the \cite{bicep2} $B$-mode 
polarization results. In this section we show that our two-component foreground
predictions are more accurate than those based on the single-MBB model of 
\cite{planckdust} over the 100-217 GHz frequency range.

% compare 100-217 GHz predictions using my model versus Planck Collaboration
% single-MBB model

@@

%striping in IRAS/IRIS versus in SFD IRAS ... planck dust map obvious striping
%%%An important difference between our maps and those of \cite{planckdust} is 
%%%our 
%%%use of SFD \verb|i100| instead of IRIS 100$\mu$m \citep{IRIS}. Residual 
%%%\IRAS~striping at levels higher than that remaining in SFD \verb|i100| is 
%%%clearly visible in the \cite{planckdust} maps.

%we actually have 6.1' arcminute resolution
%%%It is true that we have smoothed the input intensity maps for this study 
%%%to $6.1'$ FWHM, which is nominally lower resolution than the $5'$ 
%%%\cite{planckdust} maps. However, as is apparent from figure 
%%%\ref{fig:comparison}, the fact that \cite{planckdust} modeled $\beta$ at 
%%%$0.5^{\circ}$ resolution has effectively blurred their dust temperature map.

@@

\section{Conclusions}
\label{sec:conclusion}

\subsection{Single-MBB versus Two-component emission}
In both the correlation slope analysis of $\S$\ref{sec:global} and the 
goodness-of-fit analysis of $\S$\ref{sec:hier} we found that the 
best-fit \PLANCK+DIRBE two-component model (Table \ref{tab:global}, model 2) 
outperformed the best-fit single-MBB model, but by a lesser margin than found 
by FDS99 using FIRAS+DIRBE. We found $\Delta \chi^2_{nu}$= and $\Delta$

% sentence criticizing the half-degree beta single MBB model of Planck team
% in terms of the imprint that leaves on low-frequency emission 
% predictions ?

\subsection{Towards a Replacement for SFD}
%  ---> CIBA
%   ---> do i want a figure illustrating the CIBA problem at high latitude ?
%  ---> zodi
%  ---> more testing needed, in any event, to prove Planck based reddening
%       estimates outperform SFD

% should mention that one definitive improvement of this work relative
% to FDS99 is that there are uncertainty/covariances provided for
% the derived parameters !!!!
